### 2017-07-07 opsem.tex
Edits.

>>>>

\textbf{Local Context Independence} As mentioned previously, our
operational semantics does not let a transaction read its own writes.
It also does not let a transaction overwrite its own writes, due to
the premise $\dom(\stl)\cap\dom(s) = \emptyset$ on
\rulelabel{E-Delete} and \rulelabel{E-Update} rules. We refer to this
restriction as \emph{local context independence}. As such, this
restriction is easy to relax in operational semantics and the
reasoning framework presented in the next section, however, the
automation framework introduced in Sec.~\ref{sec:inference} has a
non-trivial dependence on this assumption. Nonetheless, our experience
suggests that local context independence is not a severe restriction
in practice. For instance, all 17 transactions in the TPC-C and TPC-E
benchmarks satisfy this assumption.
